### 2019-05-29 doc/chapters/trying_verify_checktx.tex
changed some sentences

We arrive at the decision that we need a smaller part to verify.
We have chosen to verify the addition with zero of Bitcoin-Ss' CurrencyUnit class as described in the next chapter.

During the examination of the checkTransaction function, we found a bug in Bitcoin-S.
You can read more about it in the next section.

@@

After so much digging and trying to understand the checkTransaction code, we found a bug even without Stainless.

>>>>

We arrive at the decision that we need a smaller part to verify.
We have chosen to verify the addition with zero of Bitcoin-Ss CurrencyUnit class as described in the next chapter.

But before that you can read about the bug we found and fixed in the next section.

@@

During the examination of the checkTransaction function, we found a bug in Bitcoin-S.
